---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# attractor

<!-- badges: start -->
<!-- badges: end -->

The goal of attractor is to discretize data in a data frame (x and y) to a matrix for fast visualizationn

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("andrie/attractor")
```
## Example

Create a strange attractor with 10 million points, then discretize to a matrix with dimensions `600 x 900`:


```{r}
library(magrittr)
library(attractor)

dat <- 
  c(-0.8, 0.4, -1.1, 0.5, -0.6, -0.1, -0.5, 0.8, 1.0, -0.3, -0.6, -0.3, -1.2, -0.3) %>% 
  strange_attractor(1e7) %>% 
  trim_quantiles(q = 0.03) %>% 
  discretize(c(600, 900))

str(dat)
```


Plot

```{r}
dat %>% 
  log1p() %>%
  recolour() %>% 
  plot()
```

Use `recolour()` to change the colours. You can use any of the colours defined by the `scales::col_numeric()` function. From the help of `?scales::col_numeric()`:

The palette argument can be any of the following:

1. A character vector of RGB or named colours. Examples: `palette()`, `c("#000000", "#0000FF", "#FFFFFF")`, `topo.colors(10)`

2. The name of an `RColorBrewer` palette, e.g. `"BuPu"` or `"Greens"`.

3. A function that receives a single value between 0 and 1 and returns a colour. Examples: `colorRamp(c("#000000", "#FFFFFF"), interpolate="spline")`.


Use the `Oranges` palette:

```{r}
dat %>% 
  log1p() %>%
  recolour("Oranges") %>%
  plot()
```

To change the background colour, specify a `zero_colour`:

```{r}
dat %>% 
  log1p() %>%
  recolour("Oranges", zero_colour = "#FFFAF6") %>%
  plot()
```

You can also invert the palette

```{r}
dat %>% 
  log1p() %>%
  recolour("Oranges", zero_colour = "grey20", invert = TRUE) %>%
  plot()
```

Try the `Spectral` palette:


```{r}
dat %>% 
  log1p() %>%
  recolour("Spectral", zero_colour = "#F60006") %>%
  plot()
```

With inversion:

```{r}
dat %>% 
  log1p() %>%
  recolour("Spectral", invert = TRUE, zero_colour = "#6272A7") %>%
  plot()

```
